Quantifying the rock-paper-scissors effect

### 2022-05-20 inst/rock_paper_scissors_monster.Rmd
typo

This gives maximum likelihood estimates of $M=0.18$ as would be
expected from the simple binomia model; the probability of a procyclic
win is about $0.625$.

>>>>

This gives maximum likelihood estimates of $M=0.18$ as would be
expected from the simple binomial model; the probability of a
procyclic win is about $0.625$.
